---
title: "What's New in RStudio 1.4"
author: "Barry DeCicco"
date: "3/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Preliminaries -----------------------------------------------------------

## Sources on the Web ----

#### From: <https://blog.rstudio.com/2020/12/02/rstudio-v1-4-preview-little-things/>

#### <https://www.youtube.com/watch?v=SdMPh5uphO0>

#### <https://www.youtube.com/watch?v=wvfI7yGZAHc>

#### <https://www.youtube.com/watch?v=mUdwE5bo7NM> (Python and RSTudio)

## Load Libraries ----

```{r Libraries}
library(tidyverse)
library(magrittr)


```

## Grouping ----

Grouping data is a very useful operation, but it isn't always obvious how data has been grouped. R Notebooks now show you information about grouping when displaying data:

```{r gouping }

mtcars %>% 
  group_by(cyl, vs)

```

## Visual Editor ----

Click the greyed out 'A' in the upper right-hand corner of the pane to switch to Visual Editor mode; click it again to switch it off.

```{r gouping }

mtcars %>% 
  group_by(cyl, vs)

```

## Insert Citation ----

In Visual Editor mode, you can insert citations,
pulling them from external website, Zotero, etc.
It will create/add to a bibliography when it does so.

## Suport for Python ----

You can now open a Python script as a file.
It uses the reticulate package.

If RStudio can't find Anaconda, it will download and 
install Miniconda from Anaconda.com.

You will have two Environment tabs (switch by a dropdown); one for R and one for Python.

In options, you can select which version of Python to use.

## Rainbow Parentheses ----

This helps track blocks of parentheses by color.




